\large{\bf Looking forwards and backwards: dynamics and genealogies of locally regulated populations }

### 2024-01-05 forwards-and-backwards.tex
one last bit

The precise sense in which we can look at ``the lineage of a sampled individual'' \revpoint{1}{2}
in the scaling limit is made clear by the introduction of the lookdown construction,
in Section~\ref{sec:lookdown}.
(For now, we can take the definition to refer to the distribution obtained
from a scaling limit of the finite-$N$ process.)
It turns out that in the scaling limit,
the process is Markovian,
and our next result identifies the ancestral lineage as a diffusion
by characterizing its generator.

>>>>

The precise sense in which we can look at ``the lineage of a sampled individual'' \revpoint{1}{2}
in the scaling limit is made clear by the introduction of the lookdown construction
in Section~\ref{sec:lookdown}:
the construction retains an unambiguous notion of ancestral lineages
through to the scaling limit,
and Theorem~\ref{thm:lookdown_convergence} shows that the these converge.
(For now, we can take the definition to refer to the distribution obtained
from a scaling limit of the finite-$N$ process.)
It turns out that in the scaling limit,
the process is Markovian,
and our next result identifies the ancestral lineage as a diffusion
by characterizing its generator.
